Executive Constraints and Civil Conflict Onset

### 2020-05-26 paper.Rmd
Fix latex compilation of manuscript
Rownames were not being added anymore causing the table to fail. I
suspect the latest minor dplyr update from the last image rebuild.

rownames(fa_pars) <- sprintf("\\textit{%s}", fa_pars$manifest)
fa_pars$manifest <- NULL

kable(fa_pars, "latex", align = "c", booktabs = T, linesep = "", escape = F,
      caption = "Posterior credible intervals for measurement model parameters") %>%
    kable_styling(latex_options = c("striped", "scale_down"), full_width = F,
                  protect_latex = F)
```

>>>>

# I absolutely hate tibbles
fa.mm <- select(fa_pars, -manifest) %>% as.matrix
rownames(fa.mm) <-sprintf("\\textit{%s}", fa_pars$manifest)

kable(fa.mm, "latex", align = "c", booktabs = T, linesep = "", escape = F,
    kable_styling(latex_options = c("striped", "scale_down"), full_width = F,
                  protect_latex = F)
```
